### 2018-11-22 Sections/optical_encoding_of_quantum_information.tex
Coherent state encoding update

This representation for qubits using coherent states is easily generalised to qudits by considering coherent states orbiting the origin of phase-space at equal angular intervals of \mbox{$2\pi/d$}, for a $d$-level qudit. The $k$th qudit basis state is then,
\begin{align}
\ket{k}_d = \ket{e^{ik/d}\alpha},
\end{align}
for \mbox{$k=0,\dots,d-1$}, where again the basis states are non-orthogonal, but closely approximate orthogonality for large $\alpha$.

>>>>

This representation for qubits using coherent states is easily generalised to qudits by considering coherent states orbiting the origin of phase-space at equal angular intervals of \mbox{$2\pi/d$}, for a $d$-level qudit. The $k$th qudit basis state is then,
\begin{align}
\ket{k}_d = \ket{\alpha e^{ik/d}},
\end{align}
for \mbox{$k=0,\dots,d-1$}, where again the basis states are non-orthogonal, but closely approximate orthogonality for large $\alpha$. The qudit value $k$ can easily be manipulated using simple phase-shift operators\index{Phase-shifts},
\begin{align}
\hat\Phi(\phi) = e^{i\phi\hat{n}},	
\end{align}
where \mbox{$\hat{n}=\hat{a}^\dag\hat{a}$} is the photon-number operator. These phases are trivially implemented in the laboratory as wavelength-scale modulations in optical path length (i.e a thin piece of glass or other transmissive material with a different refractive index).
